\hfill ~\\[-30mm] \phantom{h} \hfill\mbox{\small pre-print number if any?} \\[1cm] \vspace{13mm} \textbf{Precise predictions for same sign W-bosons scattering at the LHC}

### 2017-11-14 Draft/article.tex
Update article.tex

\date{}
\author{
Ansgar Denner$^{1\,}$,
Stefan Dittmaier$^{2\,}$,
Michele Grossi$^{3\,}$,
Alexander Karlberg$^{4\,}$, \\
Mathieu Pellen$^{1\,}$\footnote{E-mail:
  \texttt{mpellen@physik.uni-wuerzburg.de}},
Giovanni  Pelliccioli$^{5\,}$,
Michael Rauch$^{6\,}$,
J\"urgen Reuter$^{7\,}$,
Vincent Rothe$^{7\,}$, \\
Christopher Schwan$^{2\,}$,
Pascal Stienemeier$^{7\,}$,
Marco Zaro$^{8\,}$\footnote{E-mail:
  \texttt{m.zaro@nikhef.nl}}.
\\[9mm]
{\small\it
$^1$Universit\"at W\"urzburg, %
        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
{\small\it Emil-Hilb-Weg 22, \linebreak %
        97074 W\"urzburg, %
        Germany}\\[3mm]
        %
$^2${\small\it
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
{\small\it Hermann-Herder-Str.\ 3, \linebreak %
         79104 Freiburg, Germany}\\[3mm]
        %
{\small\it
$^3$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^4$Department of Physics, University of Z\"urich,} \\ %
{\small\it CH-8057
Z\"urich, Switzerland}\\[3mm]
        %
{\small\it
$^5$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^6$Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT), 
,} \\ %
{\small\it Karlsruhe, Germany}\\[3mm]
        %
{\small\it
$^7$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^8$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        }

>>>>

\date{}
\author{
Ansgar Denner$^{1\,}$,
Stefan Dittmaier$^{2\,}$,
Michele Grossi$^{3\,}{9\,}
Alexander Karlberg$^{4\,}$, \\
Mathieu Pellen$^{1\,}$\footnote{E-mail:
  \texttt{mpellen@physik.uni-wuerzburg.de}},
Giovanni  Pelliccioli$^{5\,}$,
Michael Rauch$^{6\,}$,
J\"urgen Reuter$^{7\,}$,
Vincent Rothe$^{7\,}$, \\
Christopher Schwan$^{2\,}$,
Pascal Stienemeier$^{7\,}$,
Marco Zaro$^{8\,}$\footnote{E-mail:
  \texttt{m.zaro@nikhef.nl}}.
\\[9mm]
{\small\it
$^1$Universit\"at W\"urzburg, %
        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
{\small\it Emil-Hilb-Weg 22, \linebreak %
        97074 W\"urzburg, %
        Germany}\\[3mm]
        %
$^2${\small\it
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
{\small\it Hermann-Herder-Str.\ 3, \linebreak %
         79104 Freiburg, Germany}\\[3mm]
        %
{\small\it
$^3$Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia } \\ %
{\small\it Via A. Bassi 6, \linebreak %
        27100 Pavia, %
        Italy}\\[3mm]
        %
{\small\it
$^4$Department of Physics, University of Z\"urich,} \\ %
{\small\it CH-8057
Z\"urich, Switzerland}\\[3mm]
        %
$^5${\small\it
Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino } \\ %
{\small\it Via P. Giuria 1, \linebreak %
        10125 Torino, %
        Italy}\\[3mm]
        %
{\small\it
$^6$Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT), 
,} \\ %
{\small\it Karlsruhe, Germany}\\[3mm]
        %
{\small\it
$^7$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^8$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        }
$^9$ IBM Italia s.p.a.} \\ %
{\small\it Circonvallazione Idroscalo , \linebreak %
        20090 Segrate (MI), %
        Italy}\\[3mm]
        %
